---
title: 'Some silly example using PISA'
author: "Alejandra Rodríguez Sánchez"
date: "2/9/2020"
output: word_document
mainfont: Times New Roman
fontsize: 12pt
geometry: margin=1in
bibliography: refs_miniproject.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# We call all the libraries we need
library(tidyverse)
library(ggplot2)
library(gridExtra)
library(kableExtra)
library(summarytools)
library(flextable)
library(officer)

df <- readRDS(file="D:\\PhD\\Lectures\\PISA\\germany_pisa2015")

df <- df %>% mutate(gender=ST004D01T,
                    edu_mom=ST005Q01TA,
                    edu_father=ST007Q01TA,
                    computer=ST011Q04TA,
                    books=ST013Q01TA,
                    breakfast=ST076Q01NA,
                    income=PA042Q01TA)

df <- dplyr::select(df, c(gender,edu_mom,edu_father,computer,books,breakfast,income,JOYSCIE,SCIEEFF,IMMIG,hisei,OUTHOURS,PV1MATH,PV1READ))

df <- na.omit(df)
df <- df %>% mutate(
  top_math = ifelse(PV1MATH > quantile(PV1MATH, probs = 0.75), 1, 0))
```

# Introduction
- Provide a motivation
- And make explicit what your research question is

# Background
- Some theoretical reflections
- Include some mathematical notation: $y_i = f(x_i)+\epsilon_i$
- And include some interesting reference, like @spelke2005sex

### Subsection
And you can structure your text in several sections and subsections and so on

# Data and methods
- Emphasize the method: why is suited? why not other alternatives?
1. Why is it suited?
2. How does it answer my research question?
3. What limitations does it have?
4. Why not other alternatives?

# Results
- Describe the data! (tables and plots)
- Appropriate Interpretation of results of the chosen model
- Ideally: compare different modeling alternatives

```{r table}
a <- data.frame(cat = c("Below 75th", "Above 75th", "NA", "Total"), freq(df$top_math, report.nas = FALSE, headings = T, totals = T,    cumul = FALSE))
flextable(a)
```

We could also include plots in the text very easily!

```{r plots, include=T, warning=F, echo=F, comment=F}
# Basic Bar plot
ggplot(df, aes(x=(top_math), fill=as.factor(top_math))) +
  geom_bar() +
  xlab("Top Math Performer") + 
  ylab("Count of top math performers") +
  theme(legend.position = c(0.9,0.9), legend.justification = c(1,1)) +
  scale_fill_grey(name = "Math Performer", labels = c("No", "Yes"))
```

And here is a model

```{r}
# Logit model
logit.mod <- glm(formula = top_math ~ factor(income) + factor(gender) + PV1READ, data = df, family = binomial(link="logit"))
exp(logit.mod$coefficients)
exp(confint(logit.mod))

coefs.glm <- data.frame(var = names(exp(logit.mod$coefficients)),
                   oddsratio = round(exp(logit.mod$coefficients),3),
                   LowerLimit = round(exp(confint(logit.mod))[,1],3),
                   UpperLimit = round(exp(confint(logit.mod))[,2],3))

flextable(coefs.glm)

```

and some other plots

```{r}
# document your code
# say what you are doing at each step (unlike me in most of the lectures)
ndata <- expand.grid(PV1READ = quantile(df$PV1READ), 
                     income = c("1","2","3","4","5","6"),
                     gender = c("1","2"))

# for example, obtain the predicted probabilities
preds <- predict(logit.mod, newdata = ndata, se.fit = TRUE)

invlogit <- function(x){ 1 / (1 + exp(-x)) }
plottable <- with(preds, 
                  data.frame(ndata, 
                             fit = invlogit(fit),
                             lwr = invlogit(fit + 2*se.fit),
                             upr = invlogit(fit - 2*se.fit)) )

plottable$income <- factor(plottable$income, labels= c("Less than < $A", 
                                         "$A or more but less than $B",
                                         "$B or more but less than $C",
                                         "$C or more but less than $D",
                                         "$D or more but less than $E",
                                         "$E or more"))

ggplot(plottable, aes(x = PV1READ, y = fit, col = gender, fill = gender, ymin=lwr, ymax=upr)) +
  geom_line(size = 1, alpha = 0.4) +
  geom_ribbon(alpha=0.3) +
  facet_wrap( ~ income) +
  scale_color_brewer(palette="Set1") +  # replace default colors and fill
  scale_fill_brewer(palette="Set1") +
  labs(x = "Score on Reading", y = "Probability of being top math performer", title = "Basic Plot")

```

# Discussion
- Discuss what results mean in light of the theory selected

# Conclusion
- Conclude: what did you find out?

# References